---
title: "NFL Injuries and Are They Improving?"
author: "Kristina Lau"
date: "2023-11-10"
output:
  pdf_document: default
  html_document: default
---
#Libraries
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)
library(scales)
library(ggridges)
```

#Setting up plotting theme
```{r}
theme_jason <- function(legend_pos="top", base_size=12, font=NA){
  
  # come up with some default text details
  txt <- element_text(size = base_size+3, colour = "black", face = "plain")
  bold_txt <- element_text(size = base_size+3, colour = "black", face = "bold")
  
  # use the theme_minimal() theme as a baseline
  theme_minimal(base_size = base_size, base_family = font)+
    theme(text = txt,
          # axis title and text
          axis.title.x = element_text(size = 15, hjust = 1),
          axis.title.y = element_text(size = 15, hjust = 1),
          # gridlines on plot
          panel.grid.major = element_line(linetype = 2),
          panel.grid.minor = element_line(linetype = 2),
          # title and subtitle text
          plot.title = element_text(size = 18, colour = "grey25", face = "bold"),
          plot.subtitle = element_text(size = 16, colour = "grey44"),
          
          ###### clean up!
          legend.key = element_blank(),
          # the strip.* arguments are for faceted plots
          strip.background = element_blank(),
          strip.text = element_text(face = "bold", size = 13, colour = "grey35")) +
    
    #----- AXIS -----#
    theme(
      #### remove Tick marks
      axis.ticks=element_blank(),
      
      ### legend depends on argument in function and no title
      legend.position = legend_pos,
      legend.title = element_blank(),
      legend.background = element_rect(fill = NULL, size = 0.5,linetype = 2)
      
    )
}


plot_cols <- c("#498972", "#3E8193", "#BC6E2E", "#A09D3C", "#E06E77", "#7589BC", "#A57BAF", "#4D4D4D")

```

This section will deal with cleaning up some of the variables that appear to be a bit of a mess. Some of these variables were also an issue in the NFL Big Data Bowl competition, of which my EDA there dealt with some of these, and can be found [here](https://www.kaggle.com/jaseziv83/comprehensive-cleaning-and-eda-of-all-variables).

#Stadium Type

There are `r length(unique(play_list$StadiumType))` different stadium types in the `play_list` dataset, which should immediately sound of some alarm bells.

When we inspect these levels, we can see that there are minor differences in the description of these values, in addition to spelling errors.


```{r}
play_list %>% 
  count(StadiumType) %>% 
  rename(Count = n) %>% 
  mutate(Count = comma(Count)) %>% 
  kableExtra::kable(format = "html", escape = F) %>%
  kableExtra::kable_styling("striped", full_width = F) %>% 
  kableExtra::scroll_box(height = "500px") %>%
  kableExtra::kable_styling(fixed_thead = T)
```
```


